%!TEX root = ../thesis.tex
\newchap{Conclusion}\label{sec:END}
\vspace{-1cm}
Currently, $|V_{cb}|$ is the CKM element measured with the highest relative uncertainties. Furthermore, the determination performed exploiting the semileptonic decays of B mesons showed a 7\% tension between the exclusive and the inclusive channel.\\
\\
This thesis introduces a method to perform a direct measurement of $|V_{cb}|$ at LHC through the hadronic decays of $\PW$ bosons, exploiting the semileptonic decay of $\PW$ pairs to avoid the QCD background that would make an inclusive determination an impossible task.
\\
\\
The presented analysis focused on events where the \PW pairs are produced by di-top decays and where a \PW boson decays into a muon or electron and the other into a cb quark pair.
The event selection requirements were chosen to be minimal in order to preserve the statistics.\\
\\
To discriminate the signal from the background, cutting-edge machine learning techniques were employed, particularly attention networks. 
A first attention network was built to address the jet-parton assignment problem and then adapted to the signal-background discrimination task.\\
The network was trained separately on the muon and electron signal regions and its scores were employed to extract $|V_{cb}|$ through a template fit.\\
The fit was performed using the Asimov dataset and the profile likelihood method.
The systematics uncertainties on the b/c tagging and the jet energy scale/resolution were also evaluated, obtaining a combined relative statistical precision on $|V_{cb}|$ of $5.5\%$ ($3.5\%$ Stat. + $4.4\%$ Syst.), which is less than the $7\%$ tension of the $|V_{cb}|$ puzzle.
\\
\\
In the end, the presented method is a promising prospect to tackle the $|V_{cb}|$ puzzle with a novel strategy, providing a new determination at the natural energy scale of the \PW boson which is also independent of non-perturbative QCD theoretical uncertainties.
On top of that, while in this work $|V_{cb}|$ was fitted directly as the parameter of interest, the determination could be further improved by deriving $|V_{cb}|$ from the ratio of branching fractions $|V_{cb}|^2=2\mathcal{BR}(\PW \to cb)/\mathcal{BR}(\PW \to qq)$, since it would allow cancellation in systematical uncertainties.